Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex

To gain an intuitive grasp of the decision credibility used in a statistical quorum, we can examine two toy scenarios.

In Figure \ref{fig:credible_interval}, we examine how the $90\%$ credible interval converges as more votes are collected out of a population of $100$.  A statistical quorum is achieved when the credible interval is contained entirely above the x-axis.  In this example, the latent bias of the community is that $75\%$ of the community supports the proposal while $25\%$ opposes it.

In
\begin{figure}[ht]
\centering
\includegraphics[width=0.6\textwidth]{figures/credible_interval.pdf}
\caption{.}
\label{fig:credible_interval}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/simple_majority.pdf}
\caption{.}
\label{fig:simple_majority}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/competing_proposals.pdf}
\caption{.}
\label{fig:simple_majority}
\end{subfigure}
\end{figure}

>>>>

To gain an intuitive grasp of the decision credibility used in a statistical quorum, we can examine a few toy scenarios:

In Figure \ref{fig:credible_interval}, we examine how the $90\%$ credible interval converges as more votes are collected out of a population of $100$.  A statistical quorum is achieved when the credible interval is contained entirely above zero, corresponding to a positive bias toward the proposal.  In this example, the latent bias of the community is that $75\%$ of the community supports the proposal while $25\%$ opposes it.  After approximately $35$ members have voted, a statistical quorum is achieved.

In Figure \ref{fig:simple_majority}, we examine how many affirmative votes are required from a community of size $100$ to reach a statistical quorum \textit{after} the proposal starts off with $10$ votes against it.  Initially, the $0-10$ vote tally in favor of rejecting the proposal gives the outcome over an $80\%$ credibility; however, as affirmative votes begin arriving, the credibility decreases until the `yes' votes outnumber the `no' votes.  After $21$ `yes' votes have been cast against the $10$ `no' votes, a statistical quorum of $90\%$ credibility is achieved.

In Figure \ref{fig:competing_proposals}, we examine how a set of three competing proposals gets resolved.  We simulate three proposals competing against each other in a community of size $100$, where the community has a latent bias of $75\%$, $50\%$, $25\%$ toward each of the proposals.  This scenario models what happens when a community slightly prefers the first proposal, is relatively indifferent or equivalently split on the second proposal, and slightly disproves of the third proposal.  Each member of the community casts a vote of $+0.5$, $0$, $-0.5$ for proposal 1, 2, 3, respectively.  (We have removed the stochasticity of the votes cast according to the community's latent biases in order to simplify the simulation.)  After approximately $35$ votes, we see that a statistical quorum of $90\%$ is achieved, signifying that the community's preference for proposal 1 over proposals 2, 3 is clear.

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\textwidth]{figures/credible_interval.pdf}
\caption{Convergence of the $90\%$ credible interval as more votes are cast in the population of size $100$.  A statistical quorum is achieved when the credible interval is strictly above $0$.}
\label{fig:credible_interval}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}[t]{.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/simple_majority.pdf}
\caption{Credibility of a proposal requiring a simple majority to pass: After $10$ `No' votes are initially cast, `Yes' votes arrive until a statistical quorum is achieved.}
\label{fig:simple_majority}
\end{subfigure}%
\begin{subfigure}[t]{.5\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/competing_proposals.pdf}
\caption{Credibility of a proposal competing against two other proposals: As more votes are cast according to the population's bias towards the three proposals ($75\%$, $50\%$, $25\%$), the first proposal eventually achieves a statistical quorum.}
\label{fig:competing_proposals}
\end{subfigure}
\caption{}
\end{figure}
